\section{Logic \& Number Theory}
\subsection*{Logic}
\begin{theorem}
	$$
		p\rightarrow q \equiv \neg p \lor q \equiv \neg q \rightarrow \neg p
	$$
\end{theorem}
\begin{theorem}[Basis for Contradiction]
	$$
	p\equiv \neg p \rightarrow C \qquad p\rightarrow q \equiv p \land \neg q \rightarrow C
	$$
\end{theorem}

\subsection*{Number Theory}
\begin{theorem}
	If the sum of two integers is even, their difference is also even.
\end{theorem}

\begin{theorem}
If the product of $n$ integers is odd, then all of the integers are odd.
\end{theorem}

\begin{theorem}
	If $n$ is odd, then $n^2+n+1$ is odd.
\end{theorem}

\begin{theorem}
	For all $x\in \mathbb{Z}^+$, $x^3+1$ is composite
\end{theorem}

\begin{theorem}
	For all $x,y\in \mathbb{Z}$, if $x+y$ is even, then $x$ and $y$ are both odd or both even.
\end{theorem}

\begin{theorem}
	For all $x,y\in \mathbb{R}$, if $ab$ is irrational, then either $a$ or $b$ or both are irrational.
\end{theorem}

\begin{theorem}[Sum of Arithmetic Series]
	For all $n\in \mathbb{Z}^+$, $\sum_{i=1}^n i = \frac{n(n+1)}{2}$
\end{theorem}

\begin{theorem}[Sum of Geometric Series]
	For all $n\in \mathbb{Z}^+$, $\sum_{i=1}^n r^i = \frac{r^{n+1}-1}{r-1}$
\end{theorem}

\begin{theorem}[Sum of Infinite Geometric Series]
	For all $|r| < 1$, $\sum_{i=1}^\infty r^i = \frac{1}{1-r}$
\end{theorem}

\begin{theorem}[Unique Factorization Theorem]
	For all $n\in \mathbb{Z}^+$, $n$ can be written as a product of primes in a unique way.
\end{theorem}

\begin{theorem}
	There exists infinitely many primes.
\end{theorem}

\begin{theorem}[Binomial Theorem]
	For all $n\in \mathbb{Z}^+$, $(x+y)^n = \sum_{i=0}^n \binom{n}{i} x^{n-i}y^i$
\end{theorem}

\begin{theorem}[Generalized Pigeonhole Principle]
	For all $n\in \mathbb{Z}^+$, to place $n$ objects into $k$ boxes, at least one box must contain $\lceil \frac{n}{k} \rceil$ objects.
\end{theorem}

\begin{theorem}
	For a sequence of $n$ positive integers, there exists a consecutive subsequence whos sum is devisable by $n$
\end{theorem}
